\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-11-29 doc/USER_MANUAL/manual_SPECFEM3D.tex
adds normalization option to create_movie_shakemap_AVS_DX_GMT.f90; updates movie outputs for saving displacements; updates manual in movies section

To make a surface or volume movie of the simulation, set parameters
\texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME}, and \texttt{NTSTEP\_BETWEEN\_FRAMES}
in the \texttt{Par\_file}. Turning on the movie flags, in particular
\texttt{MOVIE\_VOLUME}, produces large output files. \texttt{MOVIE\_VOLUME}
files are saved in the \texttt{LOCAL\_PATH} directory, whereas \texttt{MOVIE\_SURFACE}
output files are saved in the \texttt{in\_out\_files/OUTPUT\_FILES} directory. We
save the velocity field. The look of a movie is determined by the
half-duration of the source. The half-duration should be large enough
so that the movie does not contain frequencies that are not resolved
by the mesh, i.e., it should not contain numerical noise. This can
be accomplished by selecting a CMT \texttt{HALF\_DURATION} > 1.1 $\times$
smallest period (see figure \ref{fig:CMTSOLUTION-file}). When \texttt{MOVIE\_SURFACE}
= .\texttt{true.}, the half duration of each source in the \texttt{CMTSOLUTION}
file is replaced by

\begin{quote}
\[
\sqrt{(}\mathrm{\mathtt{HALF\_DURATIO}\mathtt{N}^{2}}+\mathrm{\mathtt{HDUR\_MOVI}\mathtt{E}^{2}})\]
\textbf{NOTE:} If \texttt{HDUR\_MOVIE} is set to 0.0, the code will
select the appropriate value of 1.1 $\times$ smallest period. As
usual, for a point source one can set \texttt{HALF\_DURATION} in the
\texttt{Par\_file} to be 0.0 and \texttt{HDUR\_MOVIE} = 0.0 to get
the highest frequencies resolved by the simulation, but for a finite
source one would keep all the \texttt{HALF\_DURATIONs} as prescribed
by the finite source model and set \texttt{HDUR\_MOVIE} = 0.0.
\end{quote}

>>>>

To make a surface or volume movie of the simulation, set parameters
\texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME}, and \texttt{NTSTEP\_BETWEEN\_FRAMES}
in the \texttt{Par\_file}. Turning on the movie flags, in particular
\texttt{MOVIE\_VOLUME}, produces large output files. \texttt{MOVIE\_VOLUME}
files are saved in the \texttt{LOCAL\_PATH} directory, whereas \texttt{MOVIE\_SURFACE}
output files are saved in the \texttt{in\_out\_files/OUTPUT\_FILES} directory. We
save the displacement field if the parameter \texttt{SAVE\_DISPLACEMENT} is set, otherwise the velocity field is saved. 
The look of a movie is determined by the
half-duration of the source. The half-duration should be large enough
so that the movie does not contain frequencies that are not resolved
by the mesh, i.e., it should not contain numerical noise. This can
be accomplished by selecting a CMT \texttt{HALF\_DURATION} > 1.1 $\times$
smallest period (see figure \ref{fig:CMTSOLUTION-file}). When \texttt{MOVIE\_SURFACE}
= .\texttt{true.}, the half duration of each source in the \texttt{CMTSOLUTION}
file is replaced by

\begin{quote}
\[
\sqrt{(}\mathrm{\mathtt{HALF\_DURATIO}\mathtt{N}^{2}}+\mathrm{\mathtt{HDUR\_MOVI}\mathtt{E}^{2}})\]
\textbf{NOTE:} If \texttt{HDUR\_MOVIE} is set to 0.0, the code will
select the appropriate value of 1.1 $\times$ smallest period. As
usual, for a point source one can set \texttt{half duration} in the
\texttt{CMTSOLUTION} file to be 0.0 and \texttt{HDUR\_MOVIE} = 0.0 in the \texttt{Par\_file} to get
the highest frequencies resolved by the simulation, but for a finite
source one would keep all the \texttt{half durations} as prescribed
by the finite source model and set \texttt{HDUR\_MOVIE} = 0.0.
\end{quote}
